\( \tool \): JavaScript IR-based Semantics Extraction Toolchain

### 2019-08-24 icse20/main.tex
Rewording

To alleviate the problem, we propose \( \tool \), a JavaScript IR-based Semantics
Extraction Toolchain. It \textit{synthesizes} a JavaScript
parser for a given grammar written in \( \bnfes \), an extended BNF
used in ECMAScript. It also \textit{automatically} extracts
semantics using rule-based compilation. Each \textit{compile rule}
describes how to convert each abstract algorithm written in a structured natural language
into functions written in \( \ires \), an Intermediate Representation
for ECMAScript. \( \tool \) synthesizes parsers from all \( \bnfes \) productions
and extracts semantics from 91.60\% of algorithm steps for five recent
ECMAScript versions. We manually extend one of the extracted semantics for
the next version of ECMAScript 2020. It passed 19,220 of 19,282 applicable tests
in Test262, the official ECMAScript conformance test suite. While extracting
the semantics using \( \tool \), we found three specification errors
and all of them are confirmed by TC 39. Moreover, we succeed to apply
our tool into an incomplete proposal as a case study.
\end{abstract}

>>>>

To alleviate the problem, we propose \( \tool \), a JavaScript IR-based Semantics
Extraction Toolchain. It \textit{synthesizes} a JavaScript
parser for a given grammar written in \( \bnfes \), an extended BNF
used in ECMAScript. It also \textit{automatically} extracts
semantics using rule-based compilation. Each \textit{compile rule}
describes how to convert each abstract algorithm written in a structured natural language
into functions written in \( \ires \), an Intermediate Representation
for ECMAScript. \( \tool \) synthesizes parsers from all \( \bnfes \) productions
and extracts semantics from 91.60\% of algorithm steps for five recent
ECMAScript versions.  We implemented a JavaScript interpreter for ECMAScript 2020
using the extracted semantics.  It passed 19,220 of 19,282 applicable tests
in Test262, the official ECMAScript conformance test suite. While extracting
the semantics using \( \tool \), we found three specification errors
and all of them were confirmed by TC 39. Moreover, we also successfully applied
our tool to an incomplete proposal as a case study.
\end{abstract}

### 2019-08-24 icse20/related.tex
Rewording

Several approaches have defined the formal semantics of JavaScript.
\citet{lambdajs} defined a core calculus of JavaScript, and expressed the
rest as desugaring.  While it presents the core JavaScript semantics in
an extension of the $\lambda$ calculus, it does not show the semantics
correspondence defined in the ECMAScript specification.  KJS~\citet{kjs} and
JaVerT~\citet{javert} defined formal semantics of JavaScript by manually converting
the ECMAScript specification to their own formal languages.  KJS mapped
ECMAScript 5.1 in the K framework~\cite{kframework}, which can be used
for program verification and analysis.  Similarly, JaVerT converts the
specification to their own IR called JSIL to make further analysis.
Our approach provides a mechanized framework to synthesize syntactic parsers and
to automatically extract semantics from the specification to \( \ires \)
using rule-based compilation technique. It significantly reduces human
efforts and also flexible for future specification updates.

>>>>

Several approaches have defined the formal semantics of JavaScript.
\citet{lambdajs} defined a core calculus of JavaScript, and expressed the
rest as desugaring.  While it presents the core JavaScript semantics in
an extension of the $\lambda$ calculus, it does not show the semantics
correspondence defined in the ECMAScript specification.  KJS~\cite{kjs} and
JaVerT~\cite{javert} defined formal semantics of JavaScript by manually converting
the ECMAScript specification to their own formal languages.  KJS mapped
ECMAScript 5.1 in the K framework~\cite{kframework}, which can be used
for program verification and analysis.  Similarly, JaVerT converts the
specification to their own IR called JSIL to make further analysis.
Our approach provides a mechanized framework to synthesize syntactic parsers and
to automatically extract semantics
using rule-based compilation technique. It significantly reduces human
efforts and also flexible for future specification updates.
